\section{Introduction}
Hiring is one of those steps in an organization that has not been automated to the fullest. As it is one of the most tiresome and repetitive tasks for an HR, it still is very important for the future of an organization. Currently the conventional method uses the company’s most important asset i.e.time in a very inefficient way as for a single candidate there are multiple steps that are to be performed which can take upto almost a day and depending upon the number of candidates it can surely become a major resource consuming process.
\par
In order to save this asset some companies have tried to automate a part or some parts of this process but not the whole process. As of now, some companies are using resume parsing\cite{bhatia2019end} thus automating the first step of hiring procedure while a fraction of these organizations use automated pre-employment tests. This is the extent of automation that has been done as of now while the interview step remains conventional and has to be done for each candidate in a very inefficient and time consuming way. What we plan to do is to automate the first two steps as well as the interviewing procedure. In this way we save a lot of time and also we can help remove the factor of biases that might occur in a conventional interview.
\par
Our solution focuses on providing all the main steps of the hiring process in a more time-efficient way thus improving the resource management effectively. Firstly candidates will submit their resumes to the automated system from where an AI-based engine using NLP\cite{sanyal2017resume} will filter out top candidates for the position they are applying for. After this the system will take an automated test that has been specified by the recruiter for the certain position. Each test will be specified by the recruiter as AI-Engine will assemble the test for each candidate differently from the questions supplied by the recruiter. In the end a list of candidates will be generated who have been successful in completing both these steps. 
\par
Automation by different companies and many solutions upto this point are readily available in the present industry but the main objective that we are aiming to choose is automating the interview process by conducting interviews in an automated environment. The automated environment will consist of a system that will act as an HR. The system will ask the questions, and the interviewee will answer those questions in front of the camera that will be streaming this video data to the system. By using the techniques of Computer Vision and Image Processing, the system will process the stream for emotion detection, analyzation of body language and the confidence level of the interviewee. Moreover the system will convert the speech of the interviewee in a textual format and will apply the techniques of Natural Language Processing (NLP) to check the relevancy scale of the interviewee’s answer with the answer that will already be fed into the system.
\subsection{Problem Statement and motivation}
Even in today’s automated world, hiring new candidates remains a manual, tedious, resource and time-consuming process containing resume shortlisting and conducting technical interviews of long queue of candidates. The whole process affords many areas which are repetitive. These areas can be automated using the principles of AI, NLP and CV. Furthermore, major companies are striving to reduce bias in this process and making sure the best person is hired. Our motivation is to automate this process in such a way that will help eradicate these problems from the hiring process, albeit making it fast and seamless.

\subsection{Overview of the Project}
The hiring process in almost every field takes a considerable amount of time as manual screening of resumes and interview process for a single candidate can take upto almost 3-4 weeks\cite{hiringstatistics} and due to the advancement in technology in the present era it seems like a big waste of time. Therefore we plan to save this important asset by automating this time-consuming and rather repetitive  process so that the workflow of the organization becomes more efficient and the time spent on recruiting new employees can be used for something productive. Our solution will require the candidates to submit their resumes from which it will filter the top candidates using an AI-based screening engine. After the resume screening process, candidates will go through an automated test which will be standardized for each position the candidate is applying for. Following the second stage of the recruiting process, the successful candidates will be notified of the scheduled interview. Afterwards the AI-engine will conduct the interview and evaluate each candidate based on its technical and behavioural metrics. AI-engine will ask questions that are designed to judge their technical and problem solving skills as well as their experience. After the final stage, the recruiter is presented with the list of candidates that have completed all the stages for further reasoning. In this way our project not only eliminates the tedious time-consuming factor of the recruiting process but also removes the biases that might occur in the manual process due to the human factor.
\subsection{Prior work}
In this modern era, humans are trying to automate every aspect of their life. This includes automating day to day work from home to their working environment. In this revolutionary world, companies are working on automating their hiring process in order to increase the number of interviews they conduct and selecting candidates who are better suitable for the job opening they are offering. This automation includes from computer-based parsing of resumes or CV’s and shortlisting the best candidates to conducting interviews of the candidates powered by some Artificial Intelligence engine that look for candidates on the basis of qualities that are specified by the companies. Some tools also offer the candidates to optimize their resumes by parsing, analyzing and suggesting.\par
Resume parsing\cite{khan2016resume} was the first emerged contribution towards automating hiring workflow. There are several softwares that are providing these services such as Zoho recruit, Resume parser by Affinda, Hiretual etc. Resume parsers basically take the resume or CV of the candidate and extract important information that is required by the HR professional. The advancement in machine learning has also provided techniques that are helpful in extracting the information and analyzing that information for shortlisting the candidates that are better suitable for the job. Natural Language Processing (NLP) is the branch of Artificial Intelligence that require machine learning in order to understand the context of written text and also to make predictions. The use of NLP has made the resume parsing process better by understanding the context and making predictions about which candidate will be better for the required job.\par
In addition to resume parsing, the use of questionnaire has also helped in automating hiring process. The AI bot takes the attempted answer by the candidates and parses and analyzes the answer for comparison with the answer that is pre fed to the AI system. Before these automated systems, the HRs used to take test from candidates on a paper and the HR had to check the technical capabilities of the candidates by manually analyzing the tests. Which was a very tiring and time-consuming process. But with these automatic answer analyzing systems, it has become easy for hiring teams to analyze the technical skills of candidates. \par
Now with the emergence of Computer Vision and Image processing the companies have implemented systems that uses Artificial Intelligence to conduct interviews. The systems ask the candidates the questions and the candidate have to answer in front of the camera that is feeding the stream to the system. The system than analyzes the video stream for emotions, confidence level and at the same time takes the user speech and converts it into Natural Language and compares the user’s speech with the pre fed answers system for relevancy level using NLP models and techniques. There are some online softwares which are providing these services.

\subsection{Our Contribution}
They are already automated systems available which parse a resume and rank the candidates from most suitable to less suitable using Natural Language Processing Models. So as a researcher, we are researching to find a solution to conduct technical video call interviews of the candidates. The solution we are looking to devise will conduct the interview of the candidate and will evaluate the candidate based on confidence level, technical skills, past experience, and problem-solving skills. We will develop a web-based application in which we will automate the hiring process starting from job advertisement to technical interview and save the recruiters from the hectic and time-wasting manual work.
