\section{Objectives of the Project}

\subsection{Industry Objectives}
Our goal in this project is to enhance the workflow of the HR department of an organization so that the primary asset of the organization i.e. time can be utilized in a more cost-effective way thus increasing the productivity of an organization.
\begin{itemize}
\item Removal of biases from the manual recruiting process.
\item Removing time wastage and maximizing efficient use of resources.
\item Decreasing manual work from the HR department which in turn would trim down the HR department.
\end{itemize}

\subsection{Research Objectives}
The main research objectives of our software solution is to go through the research work already done related to this problem and do some extra research to overcome the problems faced in the current available systems. Based on it, we will develop a software soltion that must be able to automate the hiring workflow in an efficient way.
\begin{itemize}
    \item The main aim of our project is to do research on how to analyze the technical video interview to find the confidence level based on emotions and biosignals using computer vision and image processing.
    \item Research work related to resume parsing, and Natural Language Processing will be strengthened to provide basics for our software soltion.
    \item We will do research to find a solution to use Natural Language Processing to check and rate the answers\cite{rokade2018automated} of the candidate on a relevancy scale.
    \item Research will be done to reduce the compounded error to make our system more efficient.
\end{itemize}

\subsection{Academic Objectives}
From an academic standpoint, the project will provide a learning curve for research methodologies, tools and technologies. The main academic objectives include but are not limited to: 
\begin{itemize}
    \item Integration and application of Machine Learning algorithms.
    \item Hands on experience of Computer Vision and NLP techniques.
    \item Learning how to seamlessly integrate the above technologies in a single software solution.
    \item Understanding the use of Statistics and Numerical Analysis to analyze data.
    \item Learning better task-time management with mutual collaboration.
    \item Handling real-time data and its complications.
\end{itemize}
